\documentclass[11pt,a4paper]{article}

% =============================================================================
% COVER LETTER TEMPLATE v1.0
% =============================================================================
% Conditional flags and content macros are prepended by compile-cover-letter.sh.
%
% Available flags (role — mutually exclusive):
%   \ifcryptoengineer, \ifsecurityengineer, \ifsoftwareengineer,
%   \ifappliedcrypto, \ifgeneralapplication
%
% Available flags (projects — 1-3 slots):
%   \ifprojectone, \ifprojecttwo, \ifprojectthree
%
% Available macros (injected from JSON config):
%   \CompanyName, \PositionTitle, \FocusArea
%   \PrimaryReq, \SecondaryReq, \TertiaryReq
%   \OpeningHook, \ClosingNote
%   \ProjectNameN, \ProjectURLN, \ProjectDescN  (N = 1,2,3)
% =============================================================================

% GENERATED_FLAGS_AND_MACROS_HERE

% =============================================================================
% CONDITIONAL DISPLAY HELPERS
% =============================================================================

\newcommand{\showcrypto}[1]{\ifcryptoengineer#1\fi}
\newcommand{\showsecurity}[1]{\ifsecurityengineer#1\fi}
\newcommand{\showsoftware}[1]{\ifsoftwareengineer#1\fi}
\newcommand{\showapplied}[1]{\ifappliedcrypto#1\fi}
\newcommand{\showgeneral}[1]{\ifgeneralapplication#1\fi}

% OR-logic helpers
\newcommand{\showcryptoorsecurity}[1]{\ifcryptoengineer#1\else\ifsecurityengineer#1\fi\fi}
\newcommand{\showcryptoorapplied}[1]{\ifcryptoengineer#1\else\ifappliedcrypto#1\fi\fi}
\newcommand{\showengineering}[1]{\ifcryptoengineer#1\else\ifsecurityengineer#1\else\ifsoftwareengineer#1\fi\fi\fi}
\newcommand{\shownotgeneral}[1]{\ifgeneralapplication\else#1\fi}

% =============================================================================
% PACKAGES
% =============================================================================

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.85in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage[expansion=false]{microtype}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Cover Letter -- Alexis Fernando Osorio Sarabio},
    pdfauthor={Alexis Fernando Osorio Sarabio}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% =============================================================================
% OPENING PARAGRAPH
% =============================================================================
% Each variant: identity + value proposition + company connection + specific interest
% \OpeningHook (if non-empty) replaces the first sentence with a custom hook.

\newcommand{\openingparagraph}{%

    \showcrypto{%
        \ifx\OpeningHook\empty
            As a cryptography specialist with deep expertise in post-quantum systems and
            production-grade implementations, I was immediately drawn to \textbf{\CompanyName}.%
        \else
            \OpeningHook%
        \fi{}
        \ifx\FocusArea\empty\else
            \ Your work in \textbf{\FocusArea} aligns directly with my research and engineering
            background.%
        \fi{}
        \ I have spent the last two years designing and optimizing NIST-compliant cryptographic
        protocols---including NTRU-based post-quantum key encapsulation and AES encryption
        libraries---achieving measurable performance improvements while maintaining rigorous
        security properties.
        \ifx\PositionTitle\empty\else
            \ The \textbf{\PositionTitle} role represents exactly the kind of challenge I am
            looking to take on next.%
        \fi%
    }

    \showsecurity{%
        \ifx\OpeningHook\empty
            As a security engineer specializing in cryptographic implementations, I was drawn
            to \textbf{\CompanyName} and your commitment to building resilient, standards-compliant
            security infrastructure.%
        \else
            \OpeningHook%
        \fi{}
        \ifx\FocusArea\empty\else
            \ Your focus on \textbf{\FocusArea} maps directly to my hands-on experience.%
        \fi{}
        \ I have built production-grade cryptographic systems from the ground up---implementing
        NIST-validated AES libraries, post-quantum key exchange protocols, and comprehensive
        security testing frameworks---always with an emphasis on correctness, compliance,
        and measurable security guarantees.
        \ifx\PositionTitle\empty\else
            \ I believe the \textbf{\PositionTitle} opening is a strong mutual fit.%
        \fi%
    }

    \showsoftware{%
        \ifx\OpeningHook\empty
            I am a software engineer with a security and cryptography specialization,
            and \textbf{\CompanyName}'s engineering culture caught my attention immediately.%
        \else
            \OpeningHook%
        \fi{}
        \ifx\FocusArea\empty\else
            \ Your emphasis on \textbf{\FocusArea} resonates with the kind of problems
            I most enjoy solving.%
        \fi{}
        \ My work centers on high-performance C/C++ systems with robust cryptographic
        foundations---clean architecture, comprehensive testing, and code that lasts.
        I have delivered a 20$\times$ throughput improvement in a post-quantum cryptosystem
        and a $2\times$ performance gain in an AES library, both through careful algorithmic
        analysis rather than premature optimization.
        \ifx\PositionTitle\empty\else
            \ I am excited about the \textbf{\PositionTitle} position and the technical
            challenges it entails.%
        \fi%
    }

    \showapplied{%
        \ifx\OpeningHook\empty
            As an applied cryptographer bridging theoretical research and production-quality
            software, I was compelled to reach out to \textbf{\CompanyName}.%
        \else
            \OpeningHook%
        \fi{}
        \ifx\FocusArea\empty\else
            \ Your work in \textbf{\FocusArea} sits precisely at the intersection of
            the theory and practice I care most about.%
        \fi{}
        \ My Master's research on post-quantum secure communication protocols produced
        both peer-reviewed contributions and working C++ implementations; I see no value
        in theory that cannot be deployed, nor in code that lacks formal foundations.
        \ifx\PositionTitle\empty\else
            \ The \textbf{\PositionTitle} role looks like an ideal home for that philosophy.%
        \fi%
    }

    \showgeneral{%
        \ifx\OpeningHook\empty
            I am a computer scientist and mathematician who likes to solve complex problems
            elegantly---so, to the surprise of no one, when I came across \textbf{\CompanyName}
            I was compelled to reach out.%
        \else
            \OpeningHook%
        \fi{}
        \ifx\FocusArea\empty\else
            \ Your work in \textbf{\FocusArea} is exactly the kind of challenge
            I am looking for.%
        \fi{}
        \ My background spans post-quantum cryptography, symmetric encryption, statistical
        security analysis, and web development---I am most energized when I can bring
        mathematical rigor to engineering problems that matter.%
    }
}

% =============================================================================
% REQUIREMENTS PARAGRAPH
% =============================================================================

\newcommand{\requirementsparagraph}{%
    The position emphasizes
    \ifx\PrimaryReq\empty
        technical excellence and security expertise%
    \else
        \textbf{\PrimaryReq}%
    \fi%
    \ifx\SecondaryReq\empty\else
        \ and \textbf{\SecondaryReq}%
    \fi%
    \ifx\TertiaryReq\empty\else
        \ as well as \textbf{\TertiaryReq}%
    \fi%
    . My project work provides direct evidence of these capabilities:%
}

% =============================================================================
% PROJECT DESCRIPTIONS
% =============================================================================

\newcommand{\projectdescriptions}{%
    \begin{itemize}
        \setlength{\itemsep}{4pt}

        \ifprojectone
            \item \textbf{\ProjectNameOne}
                \ (\href{\ProjectURLOne}{\texttt{GitHub}}):\\
                \ProjectDescOne
        \fi

        \ifprojecttwo
            \item \textbf{\ProjectNameTwo}
                \ (\href{\ProjectURLTwo}{\texttt{GitHub}}):\\
                \ProjectDescTwo
        \fi

        \ifprojectthree
            \item \textbf{\ProjectNameThree}
                \ (\href{\ProjectURLThree}{\texttt{GitHub}}):\\
                \ProjectDescThree
        \fi
    \end{itemize}%
}

% =============================================================================
% CLOSING PARAGRAPH
% =============================================================================

\newcommand{\closingstatement}{%
    \showengineering{%
        I am reaching out because my work philosophy resonates with what great engineering
        teams stand for: rigorous thinking, clean execution, and a genuine commitment to
        making things that work well and last. I am confident I can contribute meaningfully
        to \textbf{\CompanyName}'s goals from day one.%
    }

    \showapplied{%
        I am reaching out because I believe the best applied cryptography happens when
        theorists and engineers work in the same room---or are the same person. I would
        welcome the opportunity to bring that perspective to \textbf{\CompanyName}'s team.%
    }

    \showgeneral{%
        I am reaching out because my work philosophy and my ethics resonate with what
        \textbf{\CompanyName} stands for. I work hard to see problems as they are,
        and harder still to solve them elegantly---and I know I do my best work alongside
        people who hold themselves to the same standard.%
    }

    \ifx\ClosingNote\empty\else
        \par\ClosingNote%
    \fi

    \par
    My CV provides further detail on my technical qualifications and project experience.
    I hope you will allow me the opportunity to show how my skills and work ethic can
    contribute to your team's success. Thank you for your consideration.%
}

% =============================================================================
% DOCUMENT BODY
% =============================================================================

\begin{document}

% --- Header ---
\begin{center}
    {\LARGE \textbf{Alexis Fernando Osorio Sarabio}}\\[4pt]
    \showcrypto{\large\textit{Cryptography Engineer}}
    \showsecurity{\large\textit{Security Engineer}}
    \showsoftware{\large\textit{Software Engineer}}
    \showapplied{\large\textit{Applied Cryptographer}}
    \showgeneral{\large\textit{Computer Scientist \& Mathematician}}

    \vspace{6pt}

    \normalsize
    Mexico City, Mexico\quad$|$\quad+52 95 4128 6658\\
    \href{mailto:alexis.fernando.osorio.sarabio@gmail.com}{alexis.fernando.osorio.sarabio@gmail.com}\quad$|$\quad
    \href{https://fer-osorio.github.io/mathematical-foundations}{Portfolio}\quad$|$\quad
    \href{https://github.com/fer-osorio}{GitHub}\quad$|$\quad
    \href{https://www.linkedin.com/in/alexis-fernando-osorio-sarabio-0b755b346}{LinkedIn}
\end{center}

\vspace{10pt}
\hrule
\vspace{14pt}

% --- Date and Recipient ---
\today

\vspace{8pt}

\textbf{\CompanyName}%
\ifx\PositionTitle\empty
    \\Talent Acquisition Team%
\else
    \\Hiring Team --- \textbf{\PositionTitle}%
\fi

\vspace{8pt}

Dear \textbf{\CompanyName} Team,

\vspace{4pt}

% --- Opening ---
\openingparagraph

% --- Requirements & Projects ---
\requirementsparagraph

\projectdescriptions

% --- Closing ---
\closingstatement

\vspace{18pt}

Sincerely,

\vspace{12pt}

\textbf{Alexis Fernando Osorio Sarabio}

% --- Footer ---
\vfill
\begin{center}
    \scriptsize
    \showcrypto{\textbf{Cryptography Engineer}}
    \showsecurity{\textbf{Security Engineer}}
    \showsoftware{\textbf{Software Engineer}}
    \showapplied{\textbf{Applied Cryptographer}}
    \showgeneral{\textbf{General Application}}
    \ $\bullet$ \textbf{\CompanyName} $\bullet$ Generated \today
\end{center}

\end{document}
